Stage-Splitting a Modal Language

### 2014-10-07 paper/semantics.tex
tweaking the diagrams

The $\redonesym$ judgment takes an stage \bbone\ term\footnote{
The input to $\redonesym$ may be open on stage \bbtwo\ variables,
but the type system ensures that those must occur under a $\next$.
Consequently $\redonesym$ will never directly encounter a variable.
} to a {\em future environment} $\xi$ and a partial value $v$.  
The future environment implements
the explicit substitutions in our example---it maps fresh stage \bbtwo\
variables (which may appear inside $\next$ blocks in $v$) to
residuals. For non-staging features of \lang\ (\ref{fig:diaSemanticsCore}),
$\redonesym$ is essentially standard call-by-value evaluation, and gathers the
subterms' future environments into a single one.

At $\next~e$, in contrast, $\redonesym$ speculates into $e$ for stage~\bbone\ 
subexpressions to evaluate.  (See \ref{fig:diaSemanticsNP}.)
This is implemented by the $\redtwosym$ judgment, which takes a stage \bbtwo\ term to a residual. 
For the most part (\ref{fig:diaSemanticsSpec}), speculation simply recurs into
all subexpressions; at $\prev$, however, it resumes $\redonesym$ evaluation,
which produces a future context $\xi$ and (by canonical forms) an expression
$\next\{\hat y\}$. $\xi$ is then reified using $\reifysym$ into a series of let
bindings enclosing $\mathtt{\hat y}$.
Once speculation reduces $e$ to a residual $q$, the output of $\redonesym$ is a
fresh variable wrapped in a $\next$ block ($\next~\hat y$), along with a future
environment which maps that variable to the residual ($\hat y \mapsto q$).

>>>>

The $\redonesym$ judgment, defined in \ref{fig:diaSemantics}, takes an stage
\bbone\ term%
\footnote{ The input to $\redonesym$ may be open on stage \bbtwo\ variables, but
the type system ensures that those must occur under a $\next$. Consequently
$\redonesym$ will never directly encounter a variable.}
%
to a {\em future environment} $\xi$ and a partial value $v$. The future
environment implements the explicit substitutions in our example---it maps fresh
stage \bbtwo\ variables (which may appear inside $\next$ blocks in $v$) to
residuals. For non-staging features of \lang, $\redonesym$ is essentially
standard call-by-value evaluation, and gathers the subterms' future environments
into a single one.

\crem{Can we cut \ref{fig:diaSemanticsSpec} from the paper? Perhaps just put a
few representative rules into \ref{fig:diaSemantics}?}

At $\next~e$, in contrast, $\redonesym$ speculates into $e$ for stage~\bbone\ 
subexpressions to evaluate.  This is implemented by the $\redtwosym$ judgment,
which takes a stage \bbtwo\ term to a residual. 
For the most part (\ref{fig:diaSemanticsSpec}), speculation simply recurs into
all subexpressions; at $\prev$, however, it resumes $\redonesym$ evaluation,
which produces a future context $\xi$ and (by canonical forms) an expression
$\next\{\hat y\}$. $\xi$ is then reified using $\reifysym$ into a series of let
bindings enclosing $\mathtt{\hat y}$.
Once speculation reduces $e$ to a residual $q$, the output of $\redonesym$ is a
fresh variable wrapped in a $\next$ block ($\next~\hat y$), along with a future
environment which maps that variable to the residual ($\hat y \mapsto q$).
